---
title: "Notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting started
Clone SRA2R Project from GitHub
```{r eval=FALSE}
file > New Project... > Version Control > Git > Repository URL: https://github.com/rosachoe/SRA2R.git
```

Set Project to SRA2R

###Run Set-up
```{r eval=FALSE}
source("inst/scripts/Setup.R")
```

```{r eval=TRUE}
source("Setup.R")
```

### Download/Load SQLite database
```{r eval=FALSE} 
if(file.exists('SRAmetadb.sqlite')) {
  sra_dbname = 'SRAmetadb.sqlite'
  sra_con = dbConnect(dbDriver("SQLite"), sra_dbname)
} else {
  getSRAdbFile()
}
```

## Isolating controlled access reads
###In Terminal:
```{r eval=FALSE}
wget ftp://ftp-trace.ncbi.nlm.nih.gov/sra//reports/Metadata/SRA_Accessions.tab
```

###In R:
```{r eval=FALSE}
cmd_cut = "cut -f 1,9 $PWD/SRA_Accessions.tab"
df = read.delim(pipe(cmd_cut))
private_df = df[df$Visibility == 'controlled_access',]
```

## Usage
Getting public access reads from search
```{r eval=FALSE} 
accs = getSRA(search_terms = "breast cancer homo sapiens", sra_con = sra_con, acc_only = TRUE)
accs = accs[!(accs$run %in% private_df$Accession),"run"]
```

###Getting aligned reads
```{r eval=FALSE}
accs = getReferenceCount(accs)
```

###GenomicAlignments vs GenomicReads
```{r eval=FALSE}
"GenomicReads takes in manual input of lists for ranges and represents these locations as a table, whereas GenomicAlignments takes in files (.BAM) and converts them to a table form similar to that of GenomicReads. They can be used in conjunction, where GenomicReads would represent a constant set of locations, such as where a specific gene is located, and GenomicAlignments would represent reads from a specific organism/sample. Using the %over% function allows us to see if the samples overlap with the gene of interest."
```

###Loading Data into GenomicRanges
```{r eval=TRUE}
gr <- GRanges(seqnames = Rle(c("chr1", "chr2", "chr1", "chr3"), 
                             c(1, 3, 2, 4)), 
              ranges = IRanges(1:10, 
                               end = 7:16, 
                               names = head(letters, 10)), 
              strand = Rle(strand(c("-", "+", "*", "+", "-")), 
                           c(1, 2, 2, 3, 2)), 
              score = 1:10, 
              GC = seq(1, 0, length=10))


gr2 = GRanges(seqnames='chr1', ranges=IRanges(1,4))
```

###Loading Data into GenomicAlignments
####From File
```{r eval=TRUE}
ar = readGAlignments("ERR1189688.bam")
```
####From SRA
```{R eval=FALSE}
ar = getGAlignmentsData("ERR1189688")
```

###Example Usage
```{r eval=TRUE}
gr %over% gr2
gr2 %over% gr
which(gr %over% gr2)
which(gr2 %over% gr)
any(gr %over% ar)
any(gr2 %over% ar)
```


###Shared Files with Local Machine and Docker
```{r eval=FALSE}
1. Download file to Local Machine
2. docker-machine scp (-rcp) <filename> default:<filename>
3. docker run -v /home/docker/<filename>:<filename>
```

